### 2017-05-09 2017mergingmerges/section/05-Evaluation.tex
ref meta-repa. put "extended version" for finite streams def.

It is also possible to encode finite streams as infinite streams with an explicit end-of-stream marker (EOF) and case statements. However, this requires the fusion transform to analyse and reason about case statements and their predicates. It seems obvious that if two consumers read the same value and check if it is EOF, they will both be the same, but this is undecidable in general. By making the structure of finite streams explicit and constraining how processes use finite streams, we may be able to give more guarantees than by relying on heuristics for deciding equality of predicates.

>>>>

It is also possible to encode finite streams as infinite streams with an explicit end-of-stream marker (EOF) and case statements. However, this requires the fusion transform to analyse and reason about case statements and their predicates.
% It seems obvious that if two consumers read the same value and check if it is EOF, they will both be the same, but this is undecidable in general.
By making the structure of finite streams explicit and constraining how processes use finite streams, it is not necessary to rely on heuristics for deciding equality of predicates.

% Waffle waffle to get url on its own line
This finite stream extension is described in more detail in the appendix of the extended version of this paper, which is available at \url{http://cse.unsw.edu.au/~amosr/papers/merges.pdf}.

### 2017-05-09 2017mergingmerges/section/XX-Related.tex
Get benchmark diagram on a better page
ref meta-repa. put "extended version" for finite streams def.

%!TEX root = ../Main.tex
\section{Related work}

\TODO{Cite meta-repa \cite{ankner2013edsl}}

@@

However, short cut fusion CITE relies on inlining which, like pull-based streams, only occurs when there is a single consumer. Push-based short cut fusion systems \emph{do} exist \cite{gill1993short}, but support neither @zip@ nor @unzip@ \cite{svenningsson2002shortcut,lippmeier2013data}.

Recent work on stream fusion \cite{kiselyov2016stream} uses staged computation in a push-based system to ensure all combinators are inlined, but when streams are used multiple times this causes excessive inlining, which duplicates work.

@@

>>>>

%!TEX root = ../Main.tex
\eject
\section{Related work}

@@

However, short cut fusion \cite{gill1993short} relies on inlining which, like pull-based streams, only occurs when there is a single consumer. Push-based short cut fusion systems \emph{do} exist, notably the original foldr/build formulation, but support neither @zip@ nor @unzip@ \cite{svenningsson2002shortcut,lippmeier2013data}.

Recent work on stream fusion \cite{kiselyov2016stream} uses staged computation in a push-based system to ensure all combinators are inlined. When streams are used multiple times this causes excessive inlining, which duplicates work. This can change the semantics for effectful streams.

@@

Meta-repa \cite{ankner2013edsl} supports both array types in a similar way, using Template Haskell for code generation. It supports fusion on both array types. When arrays are used multiple times, they must be explicitly reified with a `force' operation to avoid duplication.
